Analysis of bulk void regions

### 2014-04-18 cosmic_voids.tex
Updating paper structure
Figures and analysis of fraction of halos in each environment

The study of the influence of the cosmic web on galaxy properties start 
with the seminal work of Dressler \SRKED{[reference here]} and extends to 
recent works using large observational surveys that look for signatures of 
the web into the evolution of galaxy populations. With the advention of 
more detailed observations and sophisticated computational models it is 
now within our reach to understand what physical processes dominate.

This makes  that the mass assembly history of a galaxy is deeply connected 
with its  position in the cosmic web. There is an extensive body of 
literature on the effects of the web environment on the observable 
properties of galaxies.

This environmental study is also of paramount importance to understand the 
formation of our Galaxy. In our local neighborhood, the observations of 
dwarf galaxies around the Milky Way (MW) and the Andromeda galaxy (M31) 
show filamentary and disk-like patterns that can be linked to a 
preferential infall direction, very likely connected with the cosmic web 
where the Local Group (LG) of galaxies is embedded.

In this paper we quantify the velocity shear environment of DM halo pairs
representative of the principal members of the Local Group (LG), the Milky
Way (MW) and Andromeda galaxy (M31). We perform this study in an 
unconstrained cosmological simulation from random phases in the initial 
conditions, and unlike previous works, where were used constrained 
cosmological simulations which have been setup as to reproduce the large 
scale structure of the local universe, we use directly observational 
measurements of the kinematics properties of the local group \SRKED{
[Reference here]} in order to build faithful samples of LG-like systems.

We pay special attention to the correlation of the present velocity shear 
environment with the assembly and the kinematics properties of the pairs. 
The motivation to have that focus is that it has been previously shown 
that the LG present in three different realizations of the constrained 
simulations have assembly histories biased towards early formation times 
and absence of major mergers (ratio 1:10) in the last $10$ Gyr. In the 
case of the kinematic properties, recent observational constrains to the 
galactocentric tangential velocity of M31 has enabled to establish how 
typical is the LG in a cosmological context \SRKED{[reference to 
Forero-Romero et.al 2013-1]}, that is why we focus here how a specific kind 
of host environment biases these kinematics properties.

@@

The Bolshoi simulation follows the non-linear evolution of a dark matter 
density field on a cubic volume of size $250$\hMpc sampled with $2048^3$ 
particles. The cosmological parameters in the simulation are 
$\Omega_{\rm m}=0.27$, $\Omega_{\Lambda}=0.73$, $h=0.70$, $n=0.95$ and 
$\sigma_{8}=0.82$ for the matter density, cosmological constant, 
dimensionless Hubble parameter, spectral index of primordial density 
perturbations and normalization for the power spectrum. The mass of each 
particle in the simulation is $m_{\rm p}=1.4\times 10^{8}$\hMsun.

%-------------------------------------------------------------------------
\subsection{Halos and Merger Trees}
\label{subsec:halos_merger_trees}
%-------------------------------------------------------------------------

We identify halos with two algorithms, the Friends-of-Friends \SRKED{
[reference here]} algorithm and the Bound Density Maximum algorithm. The 
constructed catalogues also provide the basis for the mass aggregation 
history studies. We also include in the catalogues information about the 
substructure.

All the results presented here must be interpreted in term of host halos, 
without any information of the substructure. In particular the merger of 
two FOF halos corresponds to the epoch of first overlap, and not to the 
fusion and/or disruption of an accreted sub-halo with a dominant halo.

The linking length is $b=0.17$ times the mean inter-particle separation. 
All objects with 20 particles or more are considered a bona fide halo and 
are included in the construction of the merger tree, this corresponds to a 
minimum halo mass of $M_{\rm min}=2.70\times 10^{9}$\hMsun in the Bolshoi 
simulation.

The halo identification for the simulation was done for XX snapshots in 
the redshift range $0<z<7$ more or less evenly spaced in look-back time.

@@

Both established schemes to quantify the cosmic web depend on continuous 
and smooth physical quantities, as the peculiar velocity field and the 
density field. In order to calculate the necessary tensors, a discretization
of the simulation volume is performed, so all the properties are reduced 
to single values associated to discrete cells. According to this, we divide 
the overall volume into $(256)^3$ cells, so each cell has an associated 
comoving cubic volume of $0.98 \mbox{ Mpc h}^{-1}$. Finally, in order to 
reduce possible effects due to the discretization process, a gaussian 
softening is performed between neighbour cells.

Once defined the numerical details about the classification schemes, we 
shall analyse the dependence on the threshold value $\lambda_{th}$ for each 
one. In Figure \ref{fig:mean_density} we show the variation of the mean 
density parameter $\delta$ with the threshold value for cells marked as one 
of the two more dominant types of environment (voids and sheets).

%.........................................................................
%FIGURE 1: Mean density for each environment
\begin{flushleft}
\begin{figure}
\centering

  \includegraphics[trim = 0mm 0mm 12mm 5mm, clip, keepaspectratio=true,
  width=0.35\textheight]{./figures/cell_types_density.pdf}

@@

  \label{fig:mean_density}
  \vspace{0.1 cm}

\end{figure}
\end{flushleft}
%.........................................................................

As was previously established by \SRKED{Hoffman et al. (2012)} and as 
can be seen in Figure \ref{fig:mean_density}, the behaviour of the 
V-web scheme is significantly more sensible to variations of the 
$\lambda_{th}$ value compared with the T-web scheme; nevertheless, the 
behaviour of the mean density parameter for voids, sheets and filaments, 
are qualitatively quite similar for the two schemes, increasing with the 
value of $\lambda_{th}$. Although we shall focus our analysis on voids 
because they are completely dominant in the visual impression of the 
cosmic web, an analogous analysis might be performed for other type of 
environments.

@@

%-------------------------------------------------------------------------
\subsection{Method to find void regions}
\label{subsec:method_voids}
%-------------------------------------------------------------------------

>>>>

Relevant information about previous works and current state of the art.

@@

The Bolshoi simulation follows the non-linear evolution of a dark matter 
density field on a cubic volume of size $250$\hMpc sampled with $2048^3$ 
particles. The cosmological parameters in the simulation are 
$\Omega_{\rm m}=0.27$, $\Omega_{\Lambda}=0.73$, $h=0.70$, $n=0.95$ and 
$\sigma_{8}=0.82$ for the matter density, cosmological constant, 
dimensionless Hubble parameter, spectral index of primordial density 
perturbations and normalization for the power spectrum. The mass of each 
particle in the simulation is $m_{\rm p}=1.4\times 10^{8}$\hMsun.
We identify halos with two algorithms, the Friends-of-Friends \SRKED{
[reference here]} algorithm and the Bound Density Maximum algorithm.

@@

Both established schemes to quantify the cosmic web depend on continuous 
and smooth physical quantities, i.e the peculiar velocity field and the 
density field. To calculate these quantities, a discretization over the 
volume of the simulation is performed, so all the properties are reduced 
to single values associated to discrete cells. According to this, we 
divide the overall volume into $(256)^3$ cells, so each cell has an 
associated comoving cubic volume of $0.98 \mbox{ Mpc h}^{-1}$. Finally, in 
order to reduce possible effects due to the discretization process, a 
gaussian softening is performed between neighbour cells.

Once defined the numerical details about both classification schemes, we
shall analyse the dependence on the threshold value $\lambda_{th}$ for 
each one. In Figure \ref{fig:median_density} we calculate the median 
contrast density for cells catalogued in each one of the types of 
environment with respect to the threshold value, where filled regions 
correspond to quartiles $Q_1$ and $Q_3$ of the samples, i.e. half of the 
cells are mapped within such regions. Moreover, we calculate fraction of
halos within each one of the defined environments based upon the FOF 
catalogue of the simulation.

As was previously established by \SRKED{Hoffman et al. (2012)} and as 
can be seen in Figure \ref{fig:median_density}, the behaviour of the 
V-web scheme is significantly more sensible to variations of the 
$\lambda_{th}$ value compared with the T-web scheme. Furthermore, taking
into account the physical origin of the T-web scheme, based upon the 
Hessian matrix, environments catalogued through this scheme have a 
well-differentiate density value for all \lth range, whereas for the V-web 
case, all regions are overlapped, specially for high \lth values and for 
high density regions, being more confuse to discern a typical density for 
each type of environment. This could be explained appealing to the 
kinematic rather than dynamic origin of the V-web, which is based upon the 
velocity shear tensor, and implying that the correspondence between 
density and peculiar velocity is less trivial for high density regions, 
what it is precisely expected for the non-linear regime.

%*************************************************************************
\section{Finding bulk voids}
\label{sec:bulk_voids}
%*************************************************************************

%*************************************************************************
\section{Statistics of voids and influence over dark matter halos}
\label{sec:statistics}
%*************************************************************************

%.........................................................................
%FIGURE 1: Median density for each environment
\begin{flushleft}
\begin{figure*}
\centering

  \includegraphics[trim = 0mm 0mm 5mm 5mm, clip, keepaspectratio=true,
  width=0.25\textheight]{./figures/median_environments_densities_Tweb.pdf}
  \includegraphics[trim = 0mm 0mm 5mm 5mm, clip, keepaspectratio=true,
  width=0.25\textheight]{./figures/median_environments_densities_Vweb.pdf}
  \includegraphics[trim = 0mm 0mm 5mm 5mm, clip, keepaspectratio=true,
  width=0.25\textheight]{./figures/halos_fraction_FOF_Tweb.pdf}
  \includegraphics[trim = 0mm 0mm 5mm 5mm, clip, keepaspectratio=true,
  width=0.25\textheight]{./figures/halos_fraction_FOF_Vweb.pdf}

@@

  \label{fig:median_density}
  \vspace{0.1 cm}

\end{figure*}
\end{flushleft}
%.........................................................................

@@
